Xor-Some Preregistered Study: Analyses

### 2021-12-02 analysis/main/04_xor-some_analysis_model_comparison.Rmd
update model comparison priors

```{r, results='hide', message=FALSE, warning=FALSE}
# Full model 
# set priors
priors <- set_prior("student_t(1, 0, 2)", class = "b")

@@

```{r, message=FALSE, warning=FALSE}
# computes the BFs 
# in favor of the prior only model over full model for XOR
bayes_factor(model_prior_comp, model_SI, silent = TRUE)
# in favor of the relevance only model over the full model for XOR
bayes_factor(model_rel_comp, model_SI, silent = TRUE)
# in favor of the relevance model over the prior model
bayes_factor(model_rel_comp, model_prior_comp, silent = TRUE)
# and in vice versa in favor of the prior model over the relevance model
bayes_factor(model_prior_comp, model_rel_comp, silent = TRUE)

# for symmetry, in favor of model without competence over full model
bayes_factor(model_rel_pri, model_SI, silent = TRUE)
bayes_factor(model_rel_pri, model_rel_comp, silent = TRUE)
bayes_factor(model_rel_pri, model_prior_comp, silent = TRUE)

@@

In order to investigate the correlation between relevance and competence we observed for "or", we also compute a model without the competence effect. Since we also observed correlation between the remaining two factors prior and relevance, perhaps the best way to disentangle the effects is to fit single-predictor models, and compate them to an intercept only model.
```{r, results='hide', message=FALSE, warning=FALSE}
# intercept only model
priors_int <- set_prior("student_t(3, 0.1, 2.5)", class = "Intercept")
model_int <- brm(target ~ 1 +
                   (1 | submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor,
                 prior = priors_int,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = 20000,
                 save_all_pars = TRUE
                 )
# single predictor models
model_rel <- brm(target ~ relevance +
                   (1 + relevance || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = 20000,
                 save_all_pars = TRUE
                 )

@@

Below, the BFs in favor of the single predictors over the intercept-only model are computed. If these are large (let's say >10), they indicate that the respective factor is important for explaining the data. 
```{r}
bayes_factor(model_pri, model_int, silent = TRUE)
bayes_factor(model_comp, model_int, silent = TRUE)
bayes_factor(model_rel, model_int, silent = TRUE)
```

Below, the BFs in favor of the two-predictor models over the respective single-predictor models are computed. If these are large, they would indicate that 1) the added model complexity is justified by a better fit to the data and 2) that the second factor is "necessary" to explain the data.
```{r}
bayes_factor(model_prior_comp, model_pri, silent = TRUE)
bayes_factor(model_prior_comp, model_comp, silent = TRUE)

bayes_factor(model_rel_pri, model_pri, silent = TRUE)
bayes_factor(model_rel_pri, model_rel, silent = TRUE)

bayes_factor(model_rel_comp, model_rel, silent = TRUE)
bayes_factor(model_rel_comp, model_comp, silent = TRUE)
```

>>>>

```{r, results='hide', message=FALSE, warning=FALSE}
# Full model 
# set priors
priors <- set_prior("student_t(1, 0, 0.25)", class = "b")

@@

```{r, message=FALSE, warning=FALSE}
# computes the BFs 
# in favor of the prior only model over full model for XOR
bf_pri_comp_full <- bayes_factor(model_prior_comp, model_SI, silent = TRUE)
# in favor of the relevance only model over the full model for XOR
bf_rel_comp_full <- bayes_factor(model_rel_comp, model_SI, silent = TRUE)
# in favor of the relevance model over the prior model
bf_rel_comp_pri_comp <- bayes_factor(model_rel_comp, model_prior_comp, silent = TRUE)
# and in vice versa in favor of the prior model over the relevance model
bf_pri_comp_rel_comp <- bayes_factor(model_prior_comp, model_rel_comp, silent = TRUE)

# for symmetry, in favor of model without competence over full model
bf_rel_pri_full <- bayes_factor(model_rel_pri, model_SI, silent = TRUE)
bf_rel_pri_rel_comp <- bayes_factor(model_rel_pri, model_rel_comp, silent = TRUE)
bf_rel_pri_pri_comp <- bayes_factor(model_rel_pri, model_prior_comp, silent = TRUE)

@@

```{r}
# try to make table by extracting numbers here

bf_results <- tribble(
  ~"Model in favor", ~"Model against", ~"BF",
  "Prior*Comp", "Pri*Comp*Rel", round(bf_pri_comp_full[1]$bf, 1),
  "Rel*Comp", "Pri*Comp*Rel", round(bf_rel_comp_full[1]$bf, 1),
  "Rel*Comp", "Pri*Comp", round(bf_rel_comp_pri_comp[1]$bf, 1),
  "Prior*Comp", "Rel*Comp", round(bf_pri_comp_rel_comp[1]$bf, 1),
  "Rel*Pri", "Pri*Comp*Rel", round(bf_rel_pri_full[1]$bf, 1),
  "Rel*Pri", "Rel*Comp", round(bf_rel_pri_rel_comp[1]$bf, 1),
  "Rel*Pri", "Pri*Comp", round(bf_rel_pri_pri_comp[1]$bf, 1)
)
bf_results

write_csv(bf_results, "../../data/main/bf_main_comparisons.csv")
```

In order to investigate the correlation between relevance and competence we observed for "or", we also compute a model without the competence effect. Since we also observed correlation between the remaining two factors prior and relevance, perhaps the best way to disentangle the effects is to fit single-predictor models, and compate them to an intercept only model.
```{r, results='hide', message=FALSE, warning=FALSE}
# intercept only model
priors_int <- set_prior("student_t(1, 0, 0.25)", class = "Intercept")
model_int <- brm(target ~ 1 +
                   (1 | submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor,
                 prior = priors_int,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = 20000,
                 save_all_pars = TRUE
                 )
# single predictor models
model_rel <- brm(target ~ relevance +
                   (1 + relevance || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.97),
                 cores = 4,
                 iter = 20000,
                 save_all_pars = TRUE
                 )

@@

Below, the BFs in favor of the single predictors over the intercept-only model are computed. If these are large (let's say >10), they indicate that the respective factor is important for explaining the data. 
```{r}
bf_pri_int <- bayes_factor(model_pri, model_int, silent = TRUE)
bf_comp_int <- bayes_factor(model_comp, model_int, silent = TRUE)
bf_rel_int <- bayes_factor(model_rel, model_int, silent = TRUE)
```

Below, the BFs in favor of the two-predictor models over the respective single-predictor models are computed. If these are large, they would indicate that 1) the added model complexity is justified by a better fit to the data and 2) that the second factor is "necessary" to explain the data.
```{r}
bf_pri_comp_pri <- bayes_factor(model_prior_comp, model_pri, silent = TRUE)
bf_pri_comp_comp <- bayes_factor(model_prior_comp, model_comp, silent = TRUE)

bf_rel_pri_pri <- bayes_factor(model_rel_pri, model_pri, silent = TRUE)
bf_rel_pri_rel <- bayes_factor(model_rel_pri, model_rel, silent = TRUE)

bf_rel_comp_rel <- bayes_factor(model_rel_comp, model_rel, silent = TRUE)
bf_rel_comp_comp <- bayes_factor(model_rel_comp, model_comp, silent = TRUE)
```

```{r}

bf_results_explore <- tribble(
  ~"Model in favor", ~"Model against", ~"BF",
  "Prior", "Int", round(bf_pri_int[1]$bf, 1),
  "Comp", "Int", round(bf_comp_int[1]$bf, 1),
  "Rel", "Int", round(bf_rel_int[1]$bf, 1),
  "Prior*Comp", "Prior", round(bf_pri_comp_pri[1]$bf, 1),
  "Prior*Comp", "Comp", round(bf_pri_comp_comp[1]$bf, 1),
  "Rel*Pri", "Prior", round(bf_rel_pri_pri[1]$bf, 1),
  "Rel*Pri", "Rel", round(bf_rel_pri_rel[1]$bf, 1),
  "Rel*Comp", "Rel", round(bf_rel_comp_rel[1]$bf, 1),
  "Rel*Comp", "Comp", round(bf_rel_comp_comp[1]$bf, 1)
)
bf_results_explore

write_csv(bf_results_explore, "../../data/main/bf_expl_comparisons.csv")

bf_results %>% 
  rbind(., bf_results_explore) %>%
  write_csv(., "../../data/main/bf_full_comparisons.csv")
```
